SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-25 scipy-1.0/paper.tex
Improvements to the Impact Now section
* added a more exact count of SciPy PyPI downloads from the year 2017,
along with a citation for the software library we used to obtain
the metric

* removed the previous examples of prominent usages of SciPy and replaced
with more compelling examples including: LIGO work and Apple / Intel shipping
SciPy in distributions

% need some better usage stats sources?
% SciPy stuff from njs blog: https://docs.google.com/spreadsheets/d/1lOLvSF0up4eZyv2ugZi-TM_GIs3gPCkGNIDKXS1Y3w4/edit#gid=406031940
From the user side, there have been at least 15 million downloads
of the SciPy manylinux wheels between the start of 2016 and May of 2018
(njs blog). The recommended source for citing SciPy is simply a reference
to the website / library itself\cite{SciPylib}, and has been cited $>3000$
times. Some of the most prominent citing articles include the IPython
publication\cite{PER-GRA:2007}, a heavily-cited Nature Biotechnology
article\cite{pmid17287757}, a dark
matter annihilitation study in the field of
cosmology\cite{1475-7516-2012-08-007}, and many of the
other major downstream software libraries in the Python scientific
computing stack.

>>>>

From the user side, there were 13,096,468 PyPI downloads
of SciPy during the year 2017\cite{pypinfo}, which is likely a vast
underestimate of total downloads given that we don't have access to the
popular Anaconda package manager download statistics. The recommended 
source for citing SciPy is simply a reference to the website / library
itself\cite{SciPylib}, and has been cited $>3000$ times. Some of the most
prominent usages of or demonstrations of credibility for SciPy include the LIGO / Virgo
scientific collaboration that lead to the observation of gravitational
waves \cite{PhysRevLett.116.061102}, and the fact that SciPy is shipped directly
with MacOS and in the Intel Distribution for Python\cite{intel-python}.
